---
output:
  md_document:
    variant: markdown_github
---

# Data Science Practical Test

```{r}
#gc() # garbage collection 
library(pacman)
p_load(tidyverse, lubridate)
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(dplyr)  
library(ggplot2)  
 
library(RColorBrewer) 
library(lubridate)  
library(xts)    
 

list.files('C:/Users/Cabous/OneDrive/Desktop/22017542/Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))


```

### Question 1

#### Loading the data

```{r}

Covid_19 <- Data(Datroot = "C:/Users/Cabous/OneDrive/Desktop/22017542/Question1/data/Covid/owid-covid-data.csv")

```

#### First plot

An interesting graph would be a graph showing the total number of cases per month, grouped by continent. We have to transform our dataset, so that it is grouped by month and continent. However, first we have to remove any NA values.

```{r}
Covid_19$total_deaths[is.na(Covid_19$total_deaths)] <- 0
Covid_19$total_cases[is.na(Covid_19$total_cases)] <- 0
Covid_19$continent[Covid_19$continent==0] <- NA

```

Now we can plot the total number of cases for each continent. We see that African countries have reported way fewer cases relative to other regions, however this could be because of a lack in transparency, or fewer covid tests.

```{r}

g <- compare_3year_trend_cases(df = Covid_19, Datesel = ymd(20200101), NYears = 3)

g

```

The second plot looks at covid related deaths for each region. Again, African countries have reported fewer deaths relative to other regions.

```{r}
g <- compare_3year_trend_deaths(df = Covid_19, Datesel = ymd(20200101), NYears = 3)

g
```



The second part of Question 1 compared the relationship between weekly ICU admissions and vaccinations. However, first removing any NA values.

```{r}
Covid_19$people_fully_vaccinated_per_hundred[is.na(Covid_19$people_fully_vaccinated_per_hundred)] <- 0
Covid_19$weekly_icu_admissions_per_million[is.na(Covid_19$weekly_icu_admissions_per_million)] <- 0
```


```{r}
Covid_19 %>% 
    
    ggplot() + 
    
    geom_line(aes(x = date, y = weekly_icu_admissions_per_million, color = continent), alpha = 0.8, 
              size = 1)
```

```{r}
Covid_19 %>% 
    
    ggplot() + 
    
    geom_line(aes(x = date, y = people_fully_vaccinated_per_hundred, color = continent), alpha = 0.8, 
              size = 1)

```

Ignoring the clear outlier in the ICU-admissions graph (probably due to an error in my code). As the majority of people became fully vaccinated around middle 2021, it appears that ICU admissions declined around the same time. This would suggest that vaccinations led to fewer ICU admissions. 



### Question 2

```{r}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(dplyr)  
library(ggplot2) 

list.files('C:/Users/Cabous/OneDrive/Desktop/22017542/Question2/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

 # Load data
London_weather <- Data_source(Datroot = "C:/Users/Cabous/OneDrive/Desktop/22017542/Question2/data/London/london_weather.csv")

```

### First plot

In my analysis, the maximum temperature recorded was between 10 and 15 Celsius, which is relatively cold compared to Cape Town (mean of 20).

```{r}

hist(London_weather$max_temp,breaks = 13, col = "blue", main = "Maximum temperature")

```
### Second plot

According to the second plot, London only has a lot days with less than 3 hours of sunshine. Thus, in order to persuade her to stay I would certainly mention this point.

```{r, message=FALSE}

hist(London_weather$sunshine ,breaks = 10, col = "yellow", main = "Hours of sunshine per day")

```



### Question 3

```{r}
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(data.table)
library(lubridate)
library(gridExtra)
library(RColorBrewer)
library(viridis)
library(magrittr)
 library(circlize)
library(cowplot)
library(ggalt)
library(fmsb)
library(ggrepel)
library(ggbump)
```

```{r}
list.files('C:/Users/Cabous/OneDrive/Desktop/22017542/Question3/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

## Loading Data

For some reason I had some trouble loading in the data from the files provided. Thus, I imported the data from Jeff Sackmann's Github.

```{r}
## Import Match Data

data <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_matches_1968.csv')

for (i in 1969:2020) {
    data <- rbind(data,
                  read_csv(paste('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_matches_', i,'.csv', sep = '')))
}

## Import Rankings Data

rankings <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_rankings_70s.csv')
rankings_80s <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_rankings_80s.csv')
rankings_90s <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_rankings_90s.csv')
rankings_00s <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_rankings_00s.csv')
rankings_10s <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_rankings_10s.csv')
rankings_20s <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_rankings_current.csv', col_names = c("ranking_date","rank", "player","points"))

## Combine
rankings <- rbind(rankings, rankings_80s, rankings_90s, rankings_00s, rankings_10s, rankings_20s)
rm(rankings_80s, rankings_90s, rankings_00s, rankings_10s, rankings_20s)


## players - needed mostly for exacting the players' date of birth 

players <- read_csv('https://raw.githubusercontent.com/JeffSackmann/tennis_atp/master/atp_players.csv',
                    col_names = c("player_id", "first_name", "last_name", "hand", "birth_date", "country_code"))


## data preprocessing 

## Change the date format (in all of the data frames).
## Also unify the naming conventions, making `player_id` stand for player ID, and `player`
## for his name and surname.

players %<>%
    mutate(birth_date = as.Date(as.character(birth_date), '%Y%m%d')) %>%
    unite(player, c("first_name", "last_name"), sep = " ")

## In the rankings data frame we will restrict it to only top 100 players for each ranking week,
## which helps significantly (~15x) reduce the size of the object.
## We will also change date format and naming convention.
## It will be convenient to add players names (from the players df) also in the rankings data frame.

rankings %<>%
    filter(rank < 101) %>%
    mutate(ranking_date = as.Date(as.character(ranking_date), '%Y%m%d')) %>%
    arrange(ranking_date, rank) %>%
    rename(player_id = player) %>%
    left_join(players %>%  select(player_id, player), by = "player_id")

```

One of the aspects I consider when finding the best player was to consider how long it took the player to reach rank 1, from the time his first game in the database was recorded.

```{r, message=FALSE}
plotTimeTaken <- plotDaysTakenToReachRank2(rankings,ranking = 1)


plotTimeTaken
```

Measured in days, Roger Federer climbed the fastest up the rankings, reaching TOP1 just after 602 days. The second fastest was Iven Lendl. Third is Djokovic with 1568 days. It took Nadal the longer to become number 1 in men’s tennis. As the chart helps us to set in the timeline, we might see that it might be because of overlapping climbing periods with Djokovic. Findings like this make us aware that we also need to consider other players’ development when assessing a player and regrets me to inform Reddit that Nadal may not be better in light of the data I have.






