---
output:
  md_document:
    variant: markdown_github
---

# Data Science Practical Test

```{r}

gc() # garbage collection 
library(pacman)
p_load(tidyverse, lubridate)
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(dplyr)  
library(ggplot2)  
install.packages("rworldmap"); library(rworldmap) 
library(RColorBrewer) 
library(hrbrthemes) 
library(lubridate)  
install.packages("dygraphs");library(dygraphs) 
library(xts)    
install.packages("gganimate");library(gganimate) 

list.files('C:/Users/Cabous/OneDrive/Desktop/22017542/Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))


```

### Question 1

#### Loading the data

```{r}

Covid_19 <- Data(Datroot = "C:/Users/Cabous/OneDrive/Desktop/22017542/Question1/data/Covid/owid-covid-data.csv")

```

#### First plot

An interesting graph would be a graph showing the total number of cases per month, grouped by continent. We have to transform our dataset, so that it is grouped by month and continent.



```{r}

plot_comparison <- compare_3year_trend(df = Covid_19, Datesel = ymd(20200101), NYears = 3)

g_total_cases

```

The second plot in the paper ...

```{r}
plot_comparison <- compare_3year_trend(df = Covid_19, Datesel = ymd(20200101), NYears = 3)

g_total_deaths 
```
The second plot in the paper ...

```{r}
Covid_19 %>% 
    
    ggplot() + 
    
    geom_line(aes(x = date, y = weekly_icu_admissions_per_million, color = continent), alpha = 0.8, 
              size = 1)
```

```{r}
Covid_19 %>% 
    
    ggplot() + 
    
    geom_line(aes(x = date, y = people_fully_vaccinated_per_hundred, color = continent), alpha = 0.8, 
              size = 1)

#As the majority of people became fully vaccinated around middle 2021,
#icu admissions declined sharply this led icu amissions
```

As the majority of people became fully vaccinated around middle 2021,
icu admissions declined sharply this led icu amissions







### Question 2

```{r}

```



### First plot

Some description here would be great.

```{r}

```



### Table




```{r, message=FALSE}

```



### Second plot

```{r, message=FALSE}

```


### Regression plot

Short overview

```{r, message=FALSE}

```