---
output:
  md_document:
    variant: markdown_github
---

# Data Science Practical Test

```{r}
#gc() # garbage collection 
library(pacman)
p_load(tidyverse, lubridate)
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(dplyr)  
library(ggplot2)  
 
library(RColorBrewer) 
library(lubridate)  
library(xts)    
 

list.files('C:/Users/Cabous/OneDrive/Desktop/22017542/Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))


```

### Question 1

#### Loading the data

```{r}

Covid_19 <- Data(Datroot = "C:/Users/Cabous/OneDrive/Desktop/22017542/Question1/data/Covid/owid-covid-data.csv")

```

#### First plot

An interesting graph would be a graph showing the total number of cases per month, grouped by continent. We have to transform our dataset, so that it is grouped by month and continent. However, first we have to remove any NA values.

```{r}
Covid_19$total_deaths[is.na(Covid_19$total_deaths)] <- 0
Covid_19$total_cases[is.na(Covid_19$total_cases)] <- 0
Covid_19$continent[Covid_19$continent==0] <- NA

```

Now we can plot the total number of cases for each continent. We see that African countries have reported way fewer cases relative to other regions, however this could be because of a lack in transparency, or fewer covid tests.

```{r}

g <- compare_3year_trend_cases(df = Covid_19, Datesel = ymd(20200101), NYears = 3)

g

```

The second plot looks at covid related deaths for each region. Again, African countries have reported fewer deaths relative to other regions.

```{r}
g <- compare_3year_trend_deaths(df = Covid_19, Datesel = ymd(20200101), NYears = 3)

g
```



The second part of Question 1 compared the relationship between weekly ICU admissions and vaccinations. However, first removing any NA values.

```{r}
Covid_19$people_fully_vaccinated_per_hundred[is.na(Covid_19$people_fully_vaccinated_per_hundred)] <- 0
Covid_19$weekly_icu_admissions_per_million[is.na(Covid_19$weekly_icu_admissions_per_million)] <- 0
```


```{r}
Covid_19 %>% 
    
    ggplot() + 
    
    geom_line(aes(x = date, y = weekly_icu_admissions_per_million, color = continent), alpha = 0.8, 
              size = 1)
```

```{r}
Covid_19 %>% 
    
    ggplot() + 
    
    geom_line(aes(x = date, y = people_fully_vaccinated_per_hundred, color = continent), alpha = 0.8, 
              size = 1)

```

Ignoring the clear outlier in the ICU-admissions graph (probably due to an error in my code). As the majority of people became fully vaccinated around middle 2021, it appears that ICU admissions declined around the same time. This would suggest that vaccinations led to fewer ICU admissions. 



### Question 2

```{r}

```



### First plot

Some description here would be great.

```{r}

```



### Table




```{r, message=FALSE}

```



### Second plot

```{r, message=FALSE}

```


### Regression plot

Short overview

```{r, message=FALSE}

```